```{r echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE,
  message = FALSE
)
```

# ropenaire

[![Build Status](https://travis-ci.org/sckott/ropenaire.svg?branch=master)](https://travis-ci.org/sckott/ropenaire)
[![Build status](https://ci.appveyor.com/api/projects/status/github/sckott/ropenaire?branch=master)](https://ci.appveyor.com/project/sckott/ropenaire)
[![codecov.io](http://codecov.io/github/sckott/ropenaire/coverage.svg?branch=master)](http://codecov.io/github/sckott/ropenaire?branch=master)

## About

**ropenaire** gives access to the [OpenAIRE RESTful API](http://api.openaire.eu/) with R. [OpenAIRE](https://www.openaire.eu/) is an open science initiative, which supports the Open Access policy of the European Commission. OpenAIRE aggregates over 12 mio publication and datasets from over 5,800 OA repositories and journals.

The API is intended for metadata discovery and exploration only. Note that the number of results returned by one query is limited to 10,000.

For bulk access, please use the [OpenAIRE OAI-PMH endpoint](http://api.openaire.eu/#cha_oai_pmh), which can be queried by [Scott's OAI-PMH client](https://github.com/sckott/oai) or [OAIHarvester](https://cran.r-project.org/web/packages/OAIHarvester/index.html).

## Installation from GitHub

```{r, eval=FALSE}
devtools::install_github("sckott/ropenaire")
```

Load `ropenaire`

```{r}
library(ropenaire)
```

## Usage 

### Projects

Search for EC-funded projects by participating institution. For example, Göttingen University has the acronym `GOE`

```{r}
roa_projects(org = "UGOE", size = 10)
```

Search projects by call id

```{r}
roa_projects(call_id = "FP7-PEOPLE-2013-IOF", size = 10)
```


### Publications

Publications from the 2nd-Generation Open Access Infrastructure for Research in Europe project, which has the grant id 283595.

```{r}
roa_pubs(fp7 = "283595", size = 10)
```

### Datasets

Search for FP7 grant-supported datasets

```{r}
roa_datasets(fp7 = "247153", size = 10)
```

Search by title keywords

```{r}
roa_datasets(title = "methane", size = 10)
```

### Get all the FP7-supported publications from a participating institution 

```{r}
roa_projects(org = "UGOE", size = 10)
```

## Meta

* Please [report any issues or bugs](https://github.com/njahn82/ropenaire/issues).
* License: MIT ©Najko Jahn
