```{r echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE,
  message = FALSE
)
```

# ropenaire

[![Build Status](https://travis-ci.org/njahn82/ropenaire.svg?branch=master)](https://travis-ci.org/njahn82/ropenaire)
[![codecov.io](http://codecov.io/github/njahn82/ropenaire/coverage.svg?branch=master)](http://codecov.io/github/njahn82/ropenaire?branch=master)

## About

The aim of this package is to provide access to the [OpenAIRE API](http://api.openaire.eu/). [OpenAIRE](https://www.openaire.eu/) provides access to grant-supported research publications and datasets. 

This package is in early developement and I am happy for contributors who wish to help me finalizing the wrapper.

## Installation from GitHub

```{r, eval=FALSE}
devtools::install_github("njahn82/ropenaire")
```

Load `ropenaire`

```{r}
library(ropenaire)
```

## Usage 

### Search for EC-funded projects by participant institutions

by acronym

```{r}
roa_projects(org = "UGOE")
```
 
### Search for FP7 grant-supported publications

```{r}
my_pubs <- roa_pubs(fp7 = "283595")
```

### Show how many of them are Open Access 

```{r}
table(my_pubs$Access)
```

## Get all the FP7-supported publications from projects an institution participates in

```{r}
ugoe <- roa_projects(org = "UGOE")
tt <- plyr::ldply(as.character(ugoe$grantID), roa_pubs)

head(tt)

table(tt$Access)
```

## Meta

* Please [report any issues or bugs](https://github.com/njahn82/ropenaire/issues).
* License: MIT


